\section{Introduction}

\subsection{Problem description}
Consider a system that manages the orders of customers in a bar. Orders are issued to a cashier, which
has two queues: one for normal users and one for VIP users. VIP users have non-preemptive priority
over normal users. Users belonging to the same queue are served according to a FIFO policy.
Orders can be of simple or compound type. Simple orders are completed directly by the cashier, with
a service rate $r_{cashier}$. Composite orders are first served by the cashier, with a service rate $r_{cashier}$, and
then are passed to the kitchen, which queues them and serves them in FIFO order, with a service rate
$r_{kitchen}$: Both normal and VIP users can issue both types of orders.

\subsection{Objectives}
% TODO update objectives based on actual results
In this analysis, the following objectives will be investigated:
\begin{itemize}
    \item relationship between the cashier service time and the overall experienced
        response time. In particular, the minimum cashier rate that guarantees a 
        given customer QoS, in terms of maximum response time.
    \item advantages, in terms of response time, of being a VIP customer.
    \item adantages and disadvantages of introducing priority head-of-line queueing
        also in the kitchen.
    \item optimal value for the ratio between VIP and normal customers in order to achieve the best overall quality of service.
    \item demonstrate that queue lengths don't depend on the ratio between the service rates.
\end{itemize}

\subsection{Performance indexes}
In order to fulfill the above-stated objectives, the following performance 
indexes will be taken into consideration:
\begin{itemize}
    \item response times for all four categories of users (normal/VIP, 
    simple/compound order), in particular their mean and 90\textsuperscript{th} 
    percentile.
    \item average queueing time for all queues.
    \item average queue length.
    \item advantage of VIP customers over normal customers as a ratio of their respective mean response times: $1-{\frac{E[R_{VIP}]}{E[R_{normal}]}}$
\end{itemize}

\subsection{Scenarios}
The following scenarios will be taken into consideration:
\begin{itemize}
    \item constant interarrival times, constant service times (only for code verification since in this scenario no queueing is possible and thus it is of no interest);
    \item exponential distribution of interarrival and service times;
    \item ``business day'': exponential distribution of interarrival and service times with varying average of the former at an hour granularity.
\end{itemize}
